Items

### 2021-08-26 proposal.Rmd
- minor changes

To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
The HEXACO model stands in the tradition of Big Five approach [@johnBigFiveTrait1999], and it represents a broad understanding of personality.
It measures overall six factors (see below), which have four specific facets each. 
Building not only on factors but also facets seems helpful because we do not expect that need for privacy will relate closely to the overarching factors.
(For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and also include specific personality facets.
<!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
In what follows, we briefly present all factors and outline how they and selected facets might relate to privacy.

@@

Notably, in addition to the Big Five the HEXACO model includes a sixth factor labeled Honesty Humility, plus a facet labeled Altruism, which together seem promising to investigate the nothing to hide argument.

>>>>

To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
The HEXACO model stands in the tradition of Big Five approach [@johnBigFiveTrait1999], and it represents a broad understanding of personality.
It measures overall six factors (see below), which have four specific facets each. 
Building not only on factors but also facets seems helpful because we do not expect that need for privacy will relate closely to the overarching factors.
(For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
Another reason for choosing the HEXACO model was that in addition to the Big Five factors the HEXACO model includes a sixth one labeled Honesty Humility, plus another facet labeled Altruism, which together seem promising to investigate the nothing to hide argument.
<!-- Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and also include specific personality facets. -->
<!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
In what follows, we briefly present all factors and outline how they and selected facets might relate to privacy.

@@
